\subsubsection{Score Calculation}

During our tests, we observed that the calculation of proofs score was
incorrect. The score of each level is needed to determine which proof
represents the chain with the most Proof of Work. Between two proofs, we only
need to calculate the score starting from their $lca$ until the tip of each
proof. Different levels are needed because the $lca$ between two proofs is only
known when the contesting proof is submitted. The security parameter $m$ needs
to be satisfied for every sub-proof $\pi[:lca]$. We ensure that this is $true$
by creating proofs of multiple levels, so that security parameter $m$ applies,
disregarding $lca$'s position.

\todo{Figure for the need of multiple levels}

Each block has a level, calculated as describe in Section(ref)
\[ level = getLevel(block) \]
Consequently, each level of the proof consists of a number of blocks
$n_{level}$. This number is the sum of blocks of level $\geq$ $level$, i.e.\
block of level $l$ are also blocks of levels $l-1$, $l-2$, etc. The
score of each level is computed as:

\[score_{level} = 2^{level} \times n_{level}\]

After running out tests for the previous implementation, we observed that
function $getLevel(block)$ of the contract was returning $block.level-1$
instead of $block.level$ resulting to incorrect score computation. This can
prevent an honest party from successfully contesting an adversarial proof,
making the contract insecure. The function was refined to return the correct
value.

