\documentclass[sigconf, anonymous]{acmart}

\usepackage{preamble}

\fancyhf{} % Remove fancy page headers
\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2019} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2019]{ACM Conference on Computer
and Communications Security}{Due 15 May 2019}{London, TBD} \acmYear{2019}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained

\begin{document}
\title{A Gas-Efficient Superlight \\Bitcoin Client in Solidity}

\begin{abstract}

Superlight clients enable the verification of proof-of-work-based blockchains
by checking only a small representative number of block headers instead of all
the block headers as done in SPV. Such clients can be embedded within other
blockchains by implementing them as smart contracts, allowing for cross-chain
verification. One such interesting instance is the consumption of Bitcoin data
within Ethereum by implementing a Bitcoin superlight client in Solidity. While
such theoretical constructions have demonstrated security and efficiency, no
practical implementation exists. In this work, we put forth the first practical
Solidity implementation of a superlight client which implements the NIPoPoW
superblocks protocol. Contrary to previous work, our Solidity smart contract
achieves sufficient gas-efficiency to allow a proof and counter-proof to fit
within the gas limit of a block, making it practical. We provide extensive
experimental measurements for gas. The optimizations that enable gas-efficiency
heavily leverage a novel technique which we term hash-and-resubmit, which
almost completely eliminates persistent storage requirements, the most
expensive operation of smart contracts in terms of gas. Instead, the contract
asks contesters to resubmit data and checks their veracity by hashing it. We
show that such techniques can be used to bring down gas costs significantly and
may have applications to other contracts. We also identify and rectify multiple
implementation security issues of previous work such as premining
vulnerabilities. Lastly, our implementation allows us to calculate concrete
cryptoeconomic parameters for the superblocks NIPoPoWs protocol and in
particular to make recommendations about the monetary value of the collateral
parameters. We provide such parameter recommendations over a variety of
liveness and adversarial bound settings.

\end{abstract}

% TODO: replace this section with code generated by the tool at
% https://dl.acm.org/ccs.cfm

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10003029.10011703</concept_id>
<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
% -- end of section to replace with generated code

\keywords{template; formatting; pickling} % TODO: replace with your keywords

\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}

\end{document}
